An Automatic Verification Framework for Software Configurations

### 2016-05-09 OSDI/learner.tex
config: learner

The goal of learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
In general, the learner module has two parts.
The first part is to learn rules to check configuration errors like
missing entry, ordering errors, and fine-grained value correlation errors. 
These errors tend to cause total system failures.
%Once the configuration file has been validated against such rules, 
%the user may choose to invoke a more sensitive constraint checker. 
The second part of the learner aims to derive 
constraints on entries to check for suspicious (\ie, anomalous) values 
that may violate standard practice (like the example~4 in
$\S$\ref{sec-motiv}).

@@

\para{A strawman solution.}
The first step of \app is to learn relations 
that must hold over multiple parts of a configuration file.
We now first present a strawman solution (employed by
previous work~\cite{santolucitoCAV, zhang14encore}) that uses 
a set of correct configuration files as a learning set, 
from which it was possible to derive rules 
that must hold with absolute certainty. 
However, this is approach is severely limiting. 
It is difficult to obtain a set of files 
that is both guaranteed to be without misconfiguration 
and large enough to learn the many rules of configuration files.
This usually requires manual verification of the learning set, 
which is prone to error.

@@

\para{Our approach.}
In \app, the rule learning mechanism is tolerant 
enough to accept a dataset {\em full of} incorrect configuration files.
Rather than manually correcting each file, 
%we observe that the files are usually incorrect in several lines.
We extend the previous formalism to run probabilistic learning
on our intermediate representations (generated by the translator).

>>>>

The goal of learner module is to derive rules and constraints from
the intermediate representation generated by the translator.
In general, the learner module has two parts.
The first part ($\S$\ref{subsec-rules}) 
is to learn rules to check configuration errors like
missing entry, ordering errors, and fine-grained value correlation errors. 
These errors tend to cause total system failures.
%Once the configuration file has been validated against such rules, 
%the user may choose to invoke a more sensitive constraint checker. 
The second part of the learner ($\S$\ref{subsec-constraints}) 
aims to derive 
constraints on entries to check for suspicious (\ie, anomalous) values 
that may violate standard practice (like the example~4 in
$\S$\ref{sec-motiv}).

@@

\para{A strawman solution.}
The first part of the learner is to learn relations 
that must hold over multiple parts of a configuration file.
We now first present a strawman solution (employed by
previous work~\cite{santolucitoCAV, zhang14encore}) that uses 
a set of correct configuration files as a learning set, 
from which it was possible to derive rules 
that must hold with absolute certainty. 
However, in practice, it is difficult to obtain a set of files 
that is both guaranteed to be without misconfiguration 
and large enough to learn many rules of configuration files.
This usually requires manual verification of the learning set, 
which is prone to error.

@@

\para{Our approach.}
In \app's leaner module, the rule learning mechanism is tolerant 
enough to accept a dataset {\em full of} incorrect configuration files.
Rather than manually correcting each file, 
%we observe that the files are usually incorrect in several lines.
We extend the previous formalism to run probabilistic learning
on our intermediate representations (generated by the translator).
